paper

### 2024-09-22 paper.qmd
.

##

@@

limrots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case0.LimROTS.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case1")
print(UPS1.Case1)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- c("Conc." , "inj")
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case1)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 50  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"  # Formula for group comparison + injections
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case1.LimROTS.rds")
```

>>>>

@@

limrots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)

saveRDS(limrots.result, "../LimROTS paper/UPS1.Case0.LimROTS.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case1")
print(UPS1.Case1)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- c("Conc." , "inj")
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case1)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 50  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc.+ inj + Conc.*inj"  # Formula for group comparison + injections
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case1, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case1.LimROTS.rds")
```
